DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
reviewed experimental objectives
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The main purpose of our experiments for set of the benchmarks described in Section~\ref{benchmarks-description} is (1) evaluate the performance of the \tool to produce stable controllers, and also (2) confirm the
stability of the synthesized controllers outside of our model in state-space and transfer-function formats.

>>>>

The main objectives of our experimental evaluation is to (1) evaluate the \tool performance 
to produce stable controllers, and also (2) confirm the stability of the synthesized digital 
controllers outside of our model, using both the transfer-function and state-space representations.
